Optimal strategies in mental rotation tasks

### 2013-05-13 man/final-project.tex
Clean up von mises model section

Another strategy is to assume a parametric shape for $S$ and fit the
appropriate parameters. Here, we assume the likelihood follows a
\emph{Von Mises} distribution:
\begin{equation}
  S(X_b, X_R) \approx \hat{S}_{VM}=\frac{h}{2\pi X_0(\kappa)}e^{\kappa\cos(R-\hat{\theta})}
\end{equation}

Where $\kappa$ is the concentration parameter, $\hat{\theta}$ is the
preferred direction, and $h$ is a scale parameter. We can fit these
parameters by minimizing the mean squared error between this PDF and
the observed values of $S$ which we are given. Then:
\begin{equation}
E[Z\ \vert \ S]\approx \int_R \hat{S}_{VM}p(R)\ \mathrm{d}R
\end{equation}

As above, we use hill-climbing, with the stopping criteria being when
we find a local maxima.

\subsubsection{Bayesian Quadrature}

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/bq_regression.pdf}
  \caption{Bayesian Quadrature}
  \label{fig:bq}
\end{figure}

>>>>

Another strategy is to assume a parametric shape for $S$ and fit the
appropriate parameters. When $h_1$ is correct, it is likely that the
function will be approximately unimodal (shapes with rotational
symmetry would be multimodal). A reasonable assumption, then, is that
the likelihood follows a ``wrapped Gaussian'', or Von Mises,
distribution:
\begin{equation}
  S(X_b, X_R) \approx h\cdot{}p(R\ \vert\ \hat{\theta}, \kappa)=\frac{h}{2\pi X_0(\kappa)}e^{\kappa\cos(R-\hat{\theta})}
\end{equation}
where $\kappa$ is the concentration parameter, $\hat{\theta}$ is the
preferred direction, and $h$ is a scale parameter. We fit these
parameters by minimizing the mean squared error between this PDF and
the computed values of $S$. To choose the sequence of rotations, we
use the same hill-climbing strategy as in the \textit{na\"ive}
model.\TODO{a better strategy would have been to compute the variance
  in parameter estimates, or something...} Figure \ref{fig:vm} shows
an example of this parametric model, prior to estimating $Z$.

\subsection{Nonparametric (Bayesian Quadrature) model}

\begin{figure}[t]
  \centering
  \includegraphics[width=\textwidth]{../figures/bq_regression.pdf}
  \caption{Nonparametric model}
  \label{fig:bq}
\end{figure}
